---
title: "`r ifelse(is.null(params$report_title), 'Default Title', params$report_title)`"
author: "`r ifelse(is.null(params$report_sub_title), 'End-Point Assay Analysis Report', params$report_sub_title)`"
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: rmarkdown_style_20241111.tex
  word_document: default
fontsize: 11pt
geometry:
  - left=0.75in
  - right=0.75in
  - top=0.5in
  - bottom=0.5in
params:
  file_name: "endpoint_assay_analysis_input.xlsx"
  report_title: "Endpoint_Assay_Output" 
  report_sub_title: "End-Point Assay Analysis Report"
  concentration_unit: "µM"
  method_init: "logistic"
  lb_if_min_gt: 0.3
  ub_if_max_lt: 0.8
  readout: "activity"
  activity_threshold: 10
  slope_threshold: 0.1
  score_label_size: 4
  x_scale: "log"
  display_type: "se_bars"
  dose_plot_sub_title: "both"
  y_axis_title: "Normalized Value"
  fig_width_in: 7.5
  fig_height_in: 5.5
---

```{r load-packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tinytex)
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  fig.align = "center"
)
library(CPDMTools)
library(readxl)
library(writexl)
library(rmarkdown)
library(stringr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(viridis)
library(flextable)
library(here)

# Turn off scientific notation
options(scipen = 999)
```


```{r data-analysis, include=FALSE}
# Import file
data <- read_excel(
  here("Test Data", "analysis_rshiny_input_files", params$file_name)
)

# Perform End-Point Assay Analysis
ctg_list <- CPDMTools::dr4pl_fit_loop(
  data_frame = data,
  concentration_unit = params$concentration_unit,
  method_init = params$method_init,
  method_robust = "squared",
  lb_if_min_gt = params$lb_if_min_gt,
  ub_if_max_lt = params$ub_if_max_lt,
  readout = params$readout,
  activity_threshold = params$activity_threshold,
  dss_type = 3,
  slope_threshold = params$slope_threshold,
  max_dss = 100
)

# Create folders
if (!file.exists(here(params$report_title, "svg"))) {
  dir.create(
    here(params$report_title, "svg"),
    recursive = TRUE
  )
}
if (!file.exists(here(params$report_title, "png"))) {
  dir.create(
    here(params$report_title, "png"),
    recursive = TRUE
  )
}
```

# Analysis Method
Dose-response curve analysis was performed using the \href{https://proxe.shinyapps.io/CPDMTools/}{\textcolor{blue}{\underline{CPDM Tools RShiny}}, where 4-parameter logistic curves were fit using the 'dr4pl' package (version `r packageVersion("dr4pl")`, `r R.version.string`) and drug sensitivity scores (DSS3) were calculated based on methods described in Yadav et al. (2014)\textsuperscript{1}. DSS3 scores were modified such that treatments with an estimated slope parameter less than `r params$slope_threshold` were assigned a score of 0.

# Results Table - All Treatments
```{r table-all,echo=FALSE, results='asis'}
CPDMTools::ctg_summary_table_all(
  ctg_list = ctg_list,
  show = "both",
  use_knit_print = FALSE
)
```

\setcounter{footnote}{1}
\footnotetext{Yadav et al. (2014). Quantitative scoring of differential drug sensitivity for individually optimized anticancer therapies. \textit{Scientific Reports}, \textit{4}(1), 5193. \href{https://doi.org/10.1038/srep05193}{https://doi.org/10.1038/srep05193}}
\setcounter{footnote}{2}

# Dose-Response Curve Plot - All Treatments
```{r dose-plot-all}
dose_plot_all <- CPDMTools::ctg_treat_plot_all(
  ctg_list = ctg_list,
  x_scale = params$x_scale,
  display_type = "se_bars",
  y_axis_title = params$y_axis_title,
  y_limits = c(0, 1.5)
)

print(dose_plot_all)

# Save plots
ggsave(
  plot = dose_plot_all,
  filename = here(
    params$report_title, "svg",
    "dose_plot_all.svg"
  ),
  width = params$fig_width_in, height = params$fig_height_in, units = "in"
)
ggsave(
  plot = dose_plot_all,
  filename = here(
    params$report_title, "png",
    "dose_plot_all.png"
  ),
  width = params$fig_width_in, height = params$fig_height_in, units = "in"
)
```

# Relative IC50 and 95% Confidence Intervals Plot - All Treatments
```{r ic50-forest}
ic50_forest <- CPDMTools::ctg_ic50_forest_plot(
  ctg_list = ctg_list,
  x_scale = params$x_scale
)

print(ic50_forest)

# Save plots
ggsave(
  plot = ic50_forest,
  filename = here(
    params$report_title, "svg",
    "ic50_forest_plot.svg"
  ),
  width = params$fig_width_in, height = params$fig_height_in, units = "in"
)
ggsave(
  plot = ic50_forest,
  filename = here(
    params$report_title, "png",
    "ic50_forest_plot.png"
  ),
  width = params$fig_width_in, height = params$fig_height_in, units = "in"
)
```

# Drug Sensitivty Score Plot - All Treatments
```{r dss-bar}
dss_bar_plot <- CPDMTools::ctg_dss_barplot(
  ctg_list = ctg_list,
  score_label_size = params$score_label_size
)

print(dss_bar_plot)

# Save plots
ggsave(
  plot = dss_bar_plot,
  filename = here(
    params$report_title, "svg",
    "dss_bar_plot.svg"
  ),
  width = params$fig_width_in, height = params$fig_height_in, units = "in"
)
ggsave(
  plot = dss_bar_plot,
  filename = here(
    params$report_title, "png",
    "dss_bar_plot.png"
  ),
  width = params$fig_width_in, height = params$fig_height_in, units = "in"
)
```

\pagebreak

```{r ind-treatments, results='asis', fig.height=4.5}
for (a in 1:nrow(ctg_list$model_parameters)) {
  
  # Print title of table
  cat(paste0("# ", ctg_list$model_parameters$treatment_name[a]))
  
  # Print summary table
  ind_tbl <- CPDMTools::ctg_summary_table_ind(
    ctg_list = ctg_list,
    treat_name = ctg_list$model_parameters$treatment_name[a]
  )
  cat(knitr::knit_print(ind_tbl))
  
  # Create individual plot
  ind_plot <- CPDMTools::ctg_treat_plot_ind(
    ctg_list = ctg_list,
    treat_name = ctg_list$model_parameters$treatment_name[a],
    x_scale = params$x_scale,
    sub_title = params$dose_plot_sub_title,
    display_type = params$display_type,
    y_axis_title = params$y_axis_title,
    y_limits = c(0, 1.5),
    n_y_axis_breaks = 7
  )
  print(ind_plot)
  
  if(a < nrow(ctg_list$model_parameters)){
    cat("\n\\pagebreak\n")
  }

  # Save plots
  ggsave(
    plot = ind_plot,
    filename =
      here(
        params$report_title, "svg",
        paste0(ctg_list$model_parameters$treatment_name[a], "_plot.svg")
      ),
    width = params$fig_width_in, height = params$fig_height_in, units = "in"
  )
  ggsave(
    plot = ind_plot,
    filename = here(
      params$report_title, "png",
      paste0(ctg_list$model_parameters$treatment_name[a], "_plot.png")
    ),
    width = params$fig_width_in, height = params$fig_height_in, units = "in"
  )
}
```

```{r export-data, include=FALSE}
# Rename list elements
names(ctg_list)[1] <- "results"
names(ctg_list)[3] <- "mono_treat_data"

# Export data to excel
writexl::write_xlsx(
  ctg_list,
  here(params$report_title, "results.xlsx")
)

```


